Trip Summary ITHIM-R

### 2020-11-23 code/producing_trips_rd/trip-summary.Rmd
Update paths

trip <- read_csv("../../data/local/mexico/mexico_city_trip.csv")
quality_check(trip)
trip_summary$Mexico <- value

@@

trip <- read_csv("../../data/local/vizag/visakhapatnam_trip.csv")
quality_check(trip)
trip_summary$Visakhapatnam <- value

>>>>

trip <- read_csv("../../data/local/mexico_city/mexico_city_trip.csv")
quality_check(trip)
trip_summary$Mexico <- value

@@

trip <- read_csv("../../data/local/vizag/vizag_trip.csv")
quality_check(trip)
trip_summary$Visakhapatnam <- value
